\Large\bf Scalable and Probabilistic Leaderless BFT Consensus through Metastability

### 2020-11-07 paper_fr.tex
French translation of the short 'Protocol Design' introduction

\section{Protocol Design}\label{sec:protocol}
We start with a non-BFT protocol called Slush and progressively build up to Snowflake and Snowball, all based on the same common majority-based metastable voting mechanism.
These protocols are single-decree consensus protocols of increasing robustness.
We provide full specifications for the protocols in this section, and defer the analysis to the next section, and present formal proofs in the appendix.

>>>>

\section{Conception du Protocole}\label{sec:protocol}
Nous partons d'un protocole non résistant au problème des généraux byzantins appelé Slush, en amenant
progressivement Snowflake et Snowball, tous basés sur le même mécanisme métastable de vote basé sur une majorité.
Ces derniers sont des protocoles de consensus à simple décret présentant plusieurs niveaux de robustesse. Nous
détaillons les caractéristiques complètes de ces protocoles dans cette section, suivie de leur analyse en section
suivante, les preuves formelles étant disponibles en annexe.

%O \section{Protocol Design}\label{sec:protocol}
%O We start with a non-BFT protocol called Slush and progressively build up to Snowflake and Snowball, all based on the same common majority-based metastable voting mechanism.
%O These protocols are single-decree consensus protocols of increasing robustness.
%O We provide full specifications for the protocols in this section, and defer the analysis to the next section, and present formal proofs in the appendix.
